%% THIS IS THE MAIN FILE %%
% Here the main arrangement of your thesis is determined. 
% In this file you read in all chapters (as separate .tex files)
% This is also the file you 'Build' with a LaTeX editor, like TeXmaker.
% The .cls file (mscThesis.cls) contains all details regarding copyrights and so on. Take a look and adjust where applicable.
% This MSc thesis standard layout is optimized for double sided printing on A4 format paper.
% Good luck and have fun with your Master Research in Applied Geophysics! Kind regards, Niels Grobbe
\documentclass[a4paper,11pt]{mscThesis}
%
%\usepackage{pifont}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage[FIGTOPCAP, hang, nooneline]{subfig}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{natbib}
\usepackage{siunitx}
%\usetikzlibrary{matrix}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{rotating}

% Gloaary
%\usepackage[plainpages=false,colorlinks]{hyperref}
%\usepackage[toc,style=treenoname,order=word,subentrycounter]{glossaries}
\usepackage{nomencl}
\makenomenclature

%\makeglossary

\mscName{Christian Reinicke Urruticoechea}
\mscDate{\today}
\mscTitle{Seismic deblending of crossline sources}
\mscSubTitle{}
\mscKeyWords{thesis, msc, subject}
%
%\mscBackPicture{2660PF3}    % eps of 21 * 29.7 cm
\mscReaderOne{Dr. Ir. G.J.A. van Groenestijn}
\mscReaderTwo{Dr. Ir. G.G.Drijkoningen}
\mscReaderThree{Dr. M. Hruska}
%\mscReaderFour{}
%
\setThesisInfo
%
\begin{document}
%
%============================= Front matter ========================================
\frontmatter %
%
% Make a hell of a lot of title pages
    \maketitle
%
% Abstract
    \nonumchap{Abstract}
Blending is a recent seismic acquisition design which allows seismic shots to interfere. Blending is beneficial in terms of data quality and acquisition costs. Current processing techniques are not capable to deal with blended data. Consequently, the blended data must be separated as if they were acquired in a conventional way. The separation technique is referred to as deblending.

This thesis reviews the 2D deblending method of \citet{Mahdad-Deblending-Method}, which is a noise prediction and subtraction method. Thus, it is demonstrated how deblending benefits from incoherent shot interference, so-called blending noise. In this context a new measure of incoherency is introduced, and 3 possibilities of incoherent blending are proposed. The effect of incoherency on the deblending quality is analyzed at the example of 2D synthetic data. The results suggest that optimal deblending quality is achieved by maximizing the incoherency of the blended acquisition.

Based on the 2D method of \citet{Mahdad-Deblending-Method} a 3D deblending method is derived. The key differences between the 2D and 3D methods are; (1) the data sorting, and (2) the coherency filter. Next, the presented method is tested on a complex synthetic data set. The results demonstrate that the method successfully deblends strong interfering events. The deblending of weak late events is not optimal yet. 

In total, the results indicate that 3D crossline blending is a potential acquisition design. With some further development 3D crossline blending is promising to become feasible as a standard acquisition design.
 

   
    \cleardoublepage
%
% table of contents, (\toc of \toclof of \tocloflot )
    %\tocloflot
\toc
%

\begin{comment}
	

% Acronyms
    \nonumchap{Acronyms} %
    %
    \begin{acronym}%
        \acro{DUT}{Delft University of Technology}%
    \end{acronym}%
    %
    \cleardublepage%
\end{comment}

% Nomenclature
    \printnomenclature
    \cleardoublepage
%
%
%============================= Main matter =========================================
%
\mainmatter
%
% Introduction
%\include{Chapters/chapter1} % notice how the reference to the introduction takes place.. It refers to the name.tex
\cleardoublepage

%
% First Part
    %\part{First Part} % you can divide your thesis into different parts, for example Theory&Modeling in part 1 and real data examples in part 2.
		%\include{Chapters/chapter2}
		
% My part
    %\part{Theory}
    	\include{Chapters/chapter-Introduction}
    	\include{Chapters/chapter4-Theory}
    	\include{Chapters/chapter7-Incoherency}
    	\include{Chapters/chapter6-3dExtension}
    	\include{Chapters/chapter-ComplexData}
    	\include{Chapters/chapter-DiscussionConclusion}
    	%\include{Chapters/chapter5-Results}
		%\include{Chapters/chapter3-Incoherency}
%\cite{Mahdad-Deblending-Method}

% Acknowledgements
    \nonumchap{Acknowledgements}%
    Thanks to my colleagues Gert-Jan, Rolf and Martijn for the great table soccer competitions, which were very inspiring for my thesis. In particular, the concept of incoherent shooting was shaped significantly during these legendary matches.

    %First of all I want to thank all the people who have participated in this project ..
    %Remember, often more people have contributed to your final thesis than you initially would think of.
    \vspace*{15mm}

    \noindent
    Delft, University of Technology \hfill \mscname\\ % change to the university where you carried out your final MSc thesis research
    \mscdate


%
% Biblio
    \bibliographystyle{apalike}
    \printbib{my_bib} % in MyBib.bib you add all your reference information, following the correct format. Sometimes, the bib file needs to be built several times, as well as the main file, before all references occur correctly in your PDF. 


%============================= Back matter =========================================
\appendix

    \chapter{The back of the thesis}

    \section{An appendix section}
    
    \todo[inline]{List of matlab functions!}

    \subsection{An appendix subsection with C++ Lisitng}

    \lstset{language=C++}
    \lstinputlisting{test.c}

    \subsection{A \matlab $ $ Listing}

    \lstset{language=matlab}
    \lstinputlisting{test.m}
    
\begin{comment}
	


    \chapter{Yet another appendix}

    \section{Another test section}

    Ok, all is well.

% Index
    \printindex%
    \cleardoublepage%
    
\end{comment}
    %\printglossary
   
	%\printnomenclature
\end{document}

